### 2018-04-12 3_encod.tex
Rename; changes from bus.

Comparing to the old \Porthos version, the algorithm of converting the program into the SSA form was also adapted for processing the plain flow-graph data structure. That is, for each node we keep track the set of its predecessors, and then, while traversing the graph in topological order, we propagate the SSA-indices for each variable defined so far, and update these indices according the rules listed above.

>>>>

Unlikely the \Porthos tool, the \mousquetaires uses the algorithm of converting the program into the SSA form was also adapted for processing the plain flow-graph data structure. That is, for each node we keep track the set of its predecessors, and then, while traversing the graph in topological order, we propagate the SSA-indices for each variable defined so far, and update these indices according the rules listed above.
